Analysis

### 2021-12-16 code/R/Analysis.Rmd
Plot evaluation results

>>>>

```{r}
d = read.csv("U:/BITCue/Projekter/TrackingFlowers/code/7temptest_eval.csv")

d %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")
```

```{r}
d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/code/8temptest_eval_THUL01.csv")

d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

```{r}
d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_2_NYAA-04_Evaluate.csv")

d2 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")
